The Shades of Racism in the Beauty Industry

### 2023-04-18 outputs/paper/paper.qmd
hide code

---
title: "The Shades of Racism in the Beauty Industry"
subtitle: "An exploration of inclusivity and tokenism within fashion and makeup"
author: 
  - Huda Sahaf
thanks: "Code and data are available at: https://github.com/hsahaf/Racism_Beauty_Industry.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper aims to investigate the history of racism in the beauty industry and how this impacts the inclusivity in the market. The complexions of models are assigned a lightness value and analyzed across 8 years. These results are compared to the foundation shade ranges across all major makeup brands across the U.S revealing a continuation of compounding racism within the industry as a whole."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```{r}
fashion_tones <-
  read.csv(
    file = "https://raw.githubusercontent.com/the-pudding/data/master/vogue/faces.csv", 
    skip = 0 
  )

@@

```{r}

### Clean Fashion Tones Dataset: 
cleaned_fashion_tones <-
  clean_names(fashion_tones)

>>>>

---
title: "The Shades of Racism in the Beauty Industry"
subtitle: "An exploration of inclusivity and tokenism within fashion and makeup industries"
author: 
  - Huda Sahaf
thanks: "Code and data are available at: https://github.com/hsahaf/Racism_Beauty_Industry.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper aims to investigate the history of racism in the beauty industry and how this impacts the inclusivity in the market. The complexions of models are assigned a lightness value and analyzed across 8 years. These results are compared to the foundation shade ranges across all major makeup brands across the U.S revealing a continuation of compounding racism within the industry as a whole."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| include: false
#| warning: false
#| message: false
fashion_tones <-
  read.csv(
    file = "https://raw.githubusercontent.com/the-pudding/data/master/vogue/faces.csv", 
    skip = 0 
  )

@@

```{r}
#| include: false
#| warning: false
#| message: false
### Clean Fashion Tones Dataset: 
cleaned_fashion_tones <-
  clean_names(fashion_tones)
